CannonRV: Measuring radial velocities with a data-driven spectral model

### 2016-12-06 paper/ms.tex
Compare the two methods
Compare the two methods for obtaining radial velocity shifts

\begin{equation}
z = {{\lambda_0 - \lambda_s} \over \lambda_s} = \sqrt{{1+\beta} \over {1-\beta}} -1 \approx \beta
\end{equation}
Where $\beta ={ v \over c} $. $v$ is the radial velocity. $\lambda_0$ and $\lambda_s$ are the wave lengths measured at the observer and the source.

@@

All spectrums in Apstar files are set to the same wavelength scale. The wavelength start at 15100.802 $\AA$ and the logarithmic wavelength grid spacing between two pixels is $6*10^{-6}$. By using (9), we find that one pixel is related to radial velocity 4144.68 m/s, which means if a=1 b= 0 and c=0, the radial velocity error in the APOGEE data is $-4144.68 m/s$

Thus we can use a, b and c to determine the radial velocity shift for the combined spectrum and each visit of the APOGEE data.
\begin{equation}
v_{shift} = {{(c-a)*v_{pixel}}\over{4\cdot(a+c-2b)}}
\end{equation}
Where $v_{shift}$ is the shift of the radial velocity in APOGEE data and $v_{pixel}$ =  4144.68 m/s.
\bigskip

@@

\includegraphics[width=170mm]{figure_1.png}
 \centerline{Fig.1 The spectrum of Star A, B, C and D}

@@

\includegraphics[width=170mm]{figure_2.png}
\bigskip

@@

We also plot delta-chi-squared vs Mean Fiber number, where delta-chi-squared is the difference between the chi-squared of the spectrum before our optimization and after. It should be bigger than 0.
\bigskip

\includegraphics[width=170mm]{figure_3.png}
\bigskip

@@

\includegraphics[width=170mm]{figure_4.png}
\bigskip

@@

\includegraphics[width=170mm]{figure_5.png}
\bigskip

@@

Also, we want to look into the spectral broadening.
Plot four stars with b closest to 1:
\bigskip

\includegraphics[width=170mm]{figure_6.png}
\bigskip

@@

From the histogram of a, b and c, we also find that sometimes b becomes much smaller than a+c, which means the spectrum is broadening due to the measurement. The resolution of the spectrum becomes lower and this is what we want to calibrate.
\bigskip
Here is the plot of the four stars with biggest a+c-b:
\bigskip

\includegraphics[width=170mm]{figure_7.png}
\bigskip

@@

To look deeper into the results, we also choose the four stars with biggest $a-c$ and biggest $c-a$. Then make another two plots:
\bigskip

\includegraphics[width=170mm]{figure_8.png}
\bigskip

@@

\includegraphics[width=170mm]{figure_9.png}
\bigskip

@@

\includegraphics[width=170mm]{figure_10.png}
\bigskip

@@

\includegraphics[width=170mm]{figure_11.png}
\bigskip

@@

\includegraphics[width=170mm]{figure_12.png}
\bigskip

@@

\includegraphics[width=170mm]{figure_13.png}
\bigskip

@@

\includegraphics[width=170mm]{figure_14.png}
\bigskip

@@

\includegraphics[width=170mm]{figure_15.png}
\bigskip

@@

\includegraphics[width=170mm]{figure_16.png}
\bigskip

@@

\includegraphics[width=170mm]{figure_17.png}
\bigskip

@@

\includegraphics[width=170mm]{d_figure_1.png}
\bigskip

@@

\includegraphics[width=170mm]{d_figure_2.png}
\bigskip

@@

\includegraphics[width=170mm]{d_figure_3.png}
\bigskip

@@

\includegraphics[width=170mm]{d_figure_4.png}
\bigskip

@@

The original histogram of radial velocity shifts for figure 11.
\bigskip

\includegraphics[width=170mm]{d_figure_5.png}
\bigskip

@@

@@

\includegraphics[width=170mm]{d_figure_6.png}
\bigskip

>>>>

\begin{equation}
z = {{\lambda_0 - \lambda_s} \over \lambda_s} = \sqrt{{1+\beta} \over {1-\beta}} -1 \approx \beta
\end{equation}
Where $\beta ={ v \over {v_{light}}} $. $v$ is the radial velocity. $\lambda_0$ and $\lambda_s$ are the wave lengths measured at the observer and the source.$v_{light}$ is the speed of light.

@@

All spectrums in Apstar files are set to the same wavelength scale. The wavelength start at 15100.802 $\AA$ and the logarithmic wavelength grid spacing between two pixels is $6*10^{-6}$. By using (9), we find that one pixel is related to radial velocity 4144.68 m/s, which means if the data spectrum moves one pixel left, the radial velocity shift in the APOGEE data is $-4144.68 m/s$. 
\\ In the following formulas, $v_{shift}$ is the shift of the radial velocity in APOGEE data and $v_{pixel}$ =  4144.68 m/s, which is the radial velocity related to one pixel. $v_{light}$ is the speed of light.

We can use a, b and c to determine the radial velocity shift for the combined spectrum and each visit of the APOGEE data.
If the parameters are a, b and c, $a\over{a+b+c}$ of the spectrum moves one pixel left, $c\over{a+b+c}$ of the spectrum moves one pixel right and $b\over{a+b+c}$ of the spectrum doesn't move. The spectrum moves one pixel left has $v_{shift} = -v_{pixel}$ and the one moves one pixel right has $v_{shift} = v_{pixel}$. ${a+c}\over2$ of the spectrum is broadening but it's included in the spectrum moves left and right. Thus the data spectrum moves ${c-a}\over{(a+b+c)}$ pixel right and we have

\begin{equation}
\log_{10} (1+{v_{shift}}/v_{light}) = {{c-a}\over{(a+b+c)}}*\log_{10}(1+{v_{pixel}}/v_{light})
\end{equation}

$v_{shift}/v_{light}$ and $v_{pixel}/v_{light}$ are small so we can use Taylor expansion. Then we have:

\begin{equation}
v_{shift} = {{(c-a)*v_{pixel}}\over{a+b+c}}
\end{equation}

@@

\begin{center}
\includegraphics[width=170mm]{figure_1.png}
\end{center}
 \centerline{Fig.1 The spectrum of Star A, B, C and D}

@@

\begin{center}
\includegraphics[width=170mm]{figure_2.png}
\end{center}

@@

We also plot delta-chi-squared vs Mean Fiber number, where delta-chi-squared is the difference between the chi-squared of the spectrum before our optimization and after. It should be bigger than 0.

\begin{center}
\includegraphics[width=170mm]{figure_3.png}
\end{center}

@@

\begin{center}
\includegraphics[width=170mm]{figure_4.png}
\end{center}

@@

\centerline{The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}

\begin{center}
\includegraphics[width=170mm]{figure_5.png}
\end{center}

@@

Also, we want to look into the spectral broadening.
Plot four stars with b closest to 1:

\begin{center}
\includegraphics[width=170mm]{figure_6.png}
\end{center}

@@

From the histogram of a, b and c, we also find that sometimes b becomes much smaller than a+c, which means the spectrum is broadening due to the measurement. The resolution of the spectrum becomes lower and this is what we want to calibrate.
\bigskip
Here is the plot of the four stars with biggest a+c-b:

\begin{center}
\includegraphics[width=170mm]{figure_7.png}
\end{center}

@@

To look deeper into the results, we also choose the four stars with biggest $a-c$ and biggest $c-a$. Then make another two plots:

\begin{center}
\includegraphics[width=170mm]{figure_8.png}
\end{center}

@@

\begin{center}
\includegraphics[width=170mm]{figure_9.png}
\end{center}

@@

\begin{center}
\includegraphics[width=170mm]{figure_10.png}
\end{center}

@@

\begin{center}
\includegraphics[width=170mm]{figure_11.png}
\end{center}

@@

\begin{center}
\includegraphics[width=170mm]{figure_12.png}
\end{center}

@@

\begin{center}
\includegraphics[width=170mm]{figure_13.png}
\end{center}

@@

\begin{center}
\includegraphics[width=170mm]{figure_14.png}
\end{center}

@@

\begin{center}
\includegraphics[width=170mm]{figure_15.png}
\end{center}

@@

\begin{center}
\includegraphics[width=170mm]{figure_16.png}
\end{center}

@@

\begin{center}
\includegraphics[width=170mm]{figure_17.png}
\end{center}

@@

\begin{center}
\includegraphics[width=170mm]{d_figure_1.png}
\end{center}

@@

\begin{center}
\includegraphics[width=170mm]{d_figure_2.png}
\end{center}

@@

\begin{center}
\includegraphics[width=170mm]{d_figure_3.png}
\end{center}

@@

\begin{center}
\includegraphics[width=170mm]{d_figure_4.png}
\end{center}

@@

The original histogram of radial velocity shifts for figure 11.

\begin{center}
\includegraphics[width=170mm]{d_figure_5.png}
\end{center}

@@

\begin{center}
\includegraphics[width=170mm]{d_figure_6.png}
\end{center}

To check which method is better, we choose the four stars with smallest abs(a-c). These four stars have abs(a-c) smaller than 0.001 and we think their radial velocity shifts are 0. We call $v_{shift} = {{(c-a)*v_{pixel}}\over{4\cdot(a+c-2b)}}$ method A and $v_{shift} = (c-a)*v_{pixel}$ method B.

First, move the data spectrum of the four stars one pixel left and the radial velocity shift should be $-v_{pixel}$= -4144.68$m/s$

\begin{center}
\includegraphics[width=170mm]{d_figure_7.png}
\end{center}

\centerline{Diagnostic Fig.7 Move the data spectrum one pixel left.}
\centerline{the radial velocity shift should be $-v_{pixel}$= -4144.68$m/s$}
\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
\bigskip

@@

Then, move the data spectrum of the four stars one pixel right and the radial velocity shift should be $v_{pixel}$= 4144.68$m/s$

\begin{center}
\includegraphics[width=170mm]{d_figure_8.png}
\end{center}

\centerline{Diagnostic Fig.8 Move the data spectrum one pixel right.}
\centerline{the radial velocity shift should be $v_{pixel}$= 4144.68$m/s$}
\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
